Khors-2023

### 2024-10-22 doc/charting/Kohrs-2023.qmd
updated list of tools to sync with format in other papers and added info to other sections

-   Virtual unconference - not a tool per se, but a nice way of networking and sharing ideas - can be used either early to brainstorm and network or later to disseminate ideas
-   COARA - fairer way of assessing research output than impact factors - Not used, just mentioned.
-   Open Science Labs - not a tool per se, but dedicated staff and organizations who works solely to contribute and assist on designing open science - study design, but they can     assist in other stages. other decentralized hubs exist such as FORRT or STEM education hub.
-   SCOSS - application for funding to be able to publish with open science standards - publication.

@@

-   Make open science necessary for the curriculum in universities (Munich university as example) and add courses that touches on openness, preregistration, etc.
-   Thesis are required to have open science elements to them. including collaborative thesis
-   Open Science requirements in the curriculum needed to hire individuals.

@@

-   Here education is the central aspect of the structure to build open science the norm in an institution
-   They suggest offering open science courses, but also integreate open science in other courses
-   They also suggest that hand-on training is the best way to learn, some ways of doing this is by making courses more interactive or have research groups go on open science        courses. Some of the courses or examples can be replications or collaborative thesis.
-   An essential part of education is allowing for spaces where researchers can work, such as journal clubs, resource hubs or hackathons.

>>>>

-   Virtual conference - networking and sharing ideas - all
-   COARA - fairer way of assessing research output than impact
    factors - dissemination
-   SCOSS - application for funding to be able to publish with open
    science standards - dissemination

@@

-   Make open science necessary for the curriculum in universities
    (Munich university as example) and add courses that touches on
    openness, preregistration, etc.
-   Thesis are required to have open science elements to them. Including
    collaborative thesis
-   Open Science requirements in the CV needed to hire individuals
-   Carefully define the scope of the project, Ensure that you have
    adequate support
-   Foster accessible discussions (Consider running "beginner" and
    "advanced" community meetings)
-   Build communities:Organize regular meetings

@@

-   Here education is the central aspect of the structure to build open
    science the norm in an institution
-   Offering open science courses, but also integreate open science in
    other courses
-   Hands-on training is the best way to learn, some ways of doing this
    is by making courses more interactive or have research groups go on
    open science courses. Some of the courses or examples can be
    replications or collaborative thesis.
-   Perform replication or meta-research studies as course projects
-   An essential part of education is allowing for spaces where
    researchers can work, such as journal clubs, resource hubs or
    hackathons.
